Flexibility of interactions depends on habitat suitability

### 2019-09-13 paper/manuscript.Rmd
add third paragraph for the discussion

@@

<!-- Suitability is not a meric of abbundances across sites (Pearce & Ferrier 2001; Sagarin et al. 2006) (Taken from Boulangeat) -->

>>>>

Although, we cannot tell with certainty how much of the effect of environmental stress is can be attributed to either niche or neutral processes it is likely that the patterns we observe are more related to the niche. 
In the one hand, it has been shown that environmental models, such as our niche factor analysis, do a poor job predicting species abundances across sites [@pearce_practical_2001; @sagarin_moving_2006]. 
It would be, therefore, somewhat naive to assume that a high habitat suitability translates directly to high species abundances. 
On the other hand, even if species abunances are correlated with suitability, we show that within a community there is a wide range of suitabilities, even for the limmited number of species we included in our analyses. 
Therefore, we might expect little or no overall effect of neutral processes on our response variable, as the abundance of some interaction partners might increasse and decreasse for others.

@@
